Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-06-10 report/report.tex
Incorporate Stiny into the Background text

Procedural techniques are, as mentioned, methods for reconstructing or creating 3D automatically, with minimal manual work required. Adding such techniques for content creation into the workflow of city reconstruction will increase the level of detail that is possible, while sacrificing accuracy to the real-world.
\textbf{(Mũller et al, 2006)} present how to accomplish this using Shape Grammar: a method for automatically and iteratively constructing 3D models based in a hierarchical set of rules.

By starting with a crude volumetric model of a building and iteratively remodeling it from a set of shape grammars, a procedural model can structure the façade, add texture and add details for windows, doors and ornaments, and so on.
Shape grammars often work from a databank of 3D models and a set of hierarchical rules for how these can be pieced together.
This creates a possible generative space of many different models that can be created from the same data and rule set, and with the induction of random fluctuations, many different models can be generated from the same dataset and rules.

%TODO: Sumarize these
Shape grammer, developed by \textbf{Stiny, 1975} (p_Par01.pdf)
Space syntax, developed by \textbf{Hillier, 1997}. Analytical method that relies on the existence of (p_Par01.pdf, SITM_Introduction.pdf)

>>>>

Procedural techniques are, as mentioned, methods for reconstructing or creating 3D automatically, with minimal manual work required.
Adding such techniques for content creation into the workflow of city reconstruction will increase the level of detail that is possible, while sacrificing accuracy to the real-world.
\textbf{(Müller et al, 2006)} present how to accomplish this using Shape Grammar: a method developed by \textbf{Stiny, 1975}, for automatically and iteratively constructing 3D models based in a hierarchical set of rules.
By starting with a crude volumetric model of a building and iteratively remodeling it from a set of shape grammars, a procedural model can structure the façade, add texture and add details for windows, doors and ornaments, and so on.
Shape grammars often work from a databank of 3D models and a set of hierarchical rules for how these can be pieced together.
This creates a possible generative space of many different models that can be created from the same data and rule set, and with the induction of random fluctuations, many different models can be generated from the same dataset and rules.

%TODO: Sumarize these
Space syntax, developed by \textbf{Hillier, 1997}. Analytical method that relies on the existence of (p_Par01.pdf, SITM_Introduction.pdf)
